Proposed Solution

### 2017-05-06 ISSTA17/secs/intro.tex
submitted version

%What do we 'plan' to do to extend this (labeled correct and incorrect)
Here we propose to extend that work, which only works on correct examples, to work on both correct and incorrect examples by building an SMT formula to find a classification model.
By learning over both correct and incorrect examples, we expect that we will be able to decrease the high false positive rate observed in ConfigC.
In order to extend ConfigC, we first provide a new description of ConfigC in terms of version space learning.
This description allows us to understand how the error reports are are produced in ConfigC.
Any extension to ConfigC must maintain the \textit{legibility} of learning - the tool must not only classify configuration files as correct or incorrect, but also identify the contributing factors (misconfigurations) to that classification.

@@

%TODO NOW NEED TO CONNECT BACK TO legibility

%legibility issue
Machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
However, many popular machine learning algorithms, such as neural nets and n-gram models, lack legibility and so are not able to provide simple justifications for their classification results.
While these classification may be effective, the lack of justification for the results limits the applicability to software analysis, where justification is often critical.
For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors so a user may fix them.

%correctness issue
Additionally, these probabilistic approaches to machine learning cannot be guaranteed to be complete, that is they are not guaranteed to always find an error if one exists.
We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
As a logical constraint system, version space learning not only provides justification of its classification results, but is has the foundation to build a completeness proof without the need for probabilistic thresholds.

As a demonstration of this algorithm, we plan to implement it to automatically verify TravisCI configurations.
The algorithm will utilize the temporal ordering on code in Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.

%evaluation plans
To test this approach in practice, we plan to implement our algorithm to check for TravisCI\footnote{\url{http://www.travis-ci.com}} configuration errors.
TravisCI is a continuous integration tool connected to Github that allows programmers to automatically run their test suite on every code update (commit).
A user adds a configuration file to the repository that enables TravisCI and specifies build conditions, such as which compiler to use, which dependencies are required, and a set of benchmarks to test.
This ensures the tool can always be automatically built correctly on a fresh machine.

>>>>

%What do we 'plan' to do to extend this (labeled correct and incorrect)
Here we propose to extend that work, which only works on correct examples, to work on both correct and incorrect examples by building an SMT formula to find a classification model.
By learning over both correct and incorrect examples, our hypothesis is that we will be able to decrease the high false positive rate observed in ConfigC, making the tool more useful to end users.
In order to extend ConfigC, we first provide a new description of ConfigC in terms of version space learning.
This description allows us to understand how the error reports are are produced in ConfigC.
Any extension to ConfigC must maintain the \textit{legibility} of learning - the tool must not only classify configuration files as correct or incorrect, but also identify the contributing factors (misconfigurations) to that classification.

%legibility issue
Legibility is a difficult property to achieve in machine learning and an active area of research~\cite{lei2016rationalizing}.
Although machine learning has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version} and invariant synthesis \cite{garg2014ice}, this requires careful selection of the algorithms.
<any popular machine learning algorithms, such as neural nets and n-gram models, notoriously lack legibility and so are not well-suited to to provide simple justifications for their classification results.
The lack of justification for the results limits the applicability to software analysis, where providing feedback to a user is critical.
For example, in the case of error detection, the system should not only report which files have errors, but also locate the errors so a user may fix them.
By using non-probabilistic version space learning, we expect to have a highly level of legibility in our learning results.

%correctness issue
Additionally, probabilistic approaches to machine learning cannot be guaranteed to be complete, that is they are not guaranteed to always find an error if one exists.
We use version space learning to address the need for a formal completeness guarantee in an automated model generation for verification.
Version space learning is a technique for logical constraint classification~\cite{mitchell82}.
As a logical constraint system, version space learning not only provides justification of its classification results, but is has the foundation to build a completeness proof without the need for probabilistic thresholds.

@@

%evaluation plans
To test this approach in practice, we plan to implement our algorithm to check for TravisCI\footnote{\url{http://www.travis-ci.com}} configuration errors.
TravisCI is a continuous integration tool connected to Github that allows programmers to automatically run their test suite on every code update (commit).
A user adds a configuration file to the repository that enables TravisCI and specifies build conditions, such as which compiler to use, which dependencies are required, and a set of benchmarks to test.
This ensures the tool can always be automatically built correctly on a fresh machine.
The algorithm will utilize the temporal ordering on code in Github histories to allow us to detect potential build errors without actually building, saving valuable programmer and server time.

### 2017-05-06 ISSTA17/secs/limits.tex
expaneded version of FMCAD for ISSTA
notes
submitted version

\section{Limitations}

%\subsection{Unsatisfiability}
Note we have made two assumptions in Eq. \ref{eq:E1}; first that the summary $P_t$ sufficently detailed, i.e. contains every piece of information that might lead to a build error, and second that the model $M(P_t)$ will learn all relations that might lead to a build error, i.e. has a templete for all types of errors.
While these are the strong assumptions - our algorithm is able to detect cases where these assumptions are not met.
If we cannot find a solution for Eq. \ref{eq:PE}, it means either $P_t$ or $M(P_t)$ has been underspecified.
It is then the user's responsibility to expand the definitions accordingly.

\subsection{Trusted Base}
In addition to the completeness of $P_t$ and $M(P_t)$, we must pick a trusted base.
Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
Since version space learning is (generally) intolerant of noise, we require that
$P_t = P_{t'} \implies S(P_t) = S(P_{t'})$.

>>>>

\section{Properties of Temporal Learning}

We have made two assumptions in Eq. \ref{eq:E1}; first that the summary $P_t$ sufficiently detailed, i.e. contains every piece of information that might lead to a build error, and second that the model $M(P_t)$ will learn all relations that might lead to a build error, i.e. has a template for all types of errors.
While these are the strong assumptions - our algorithm is able to detect cases where these assumptions are not met.
If we cannot find a solution for Eq. \ref{eq:PE}, it means either $P_t$ or $M(P_t)$ has been underspecified and is insufficiently detailed.
It is then the user's responsibility to expand the definitions accordingly.

In addition to the sufficient detail of $P_t$ and $M(P_t)$, we must pick a trusted base.
Since it is possible for TravisCI to have bugs, it is possible that between versions of TravisCI, two identical program summaries may have different build statuses.
Since version space learning is (generally) intolerant of noise, we require that
$P_t = P_{t'} \implies S(P_t) = S(P_{t'})$.
If we allow for noisy data, for example in the case that it is not possible to identify a trusted base, this predicate will no longer hold.
This situation would require a noise tolerant version space learning~\cite{hong1997generalized}, though this may degrade the completeness guarantees.

Picking the right assumptions upon which to build a completeness and soundness proof remain future work, either with a trusted base, or in the noisy context.
Choosing the right assumption and building these proofs are a valuable direction, as it will allow us to identify which parts of the model and training set are most important to ensure coverage of the system.

### 2017-05-06 ISSTA17/secs/related.tex
notes
submitted version

Configuration verification has been considered a promising way  
to tackle misconfiguration problems~\cite{xu15systems}.
Nevertheless, a practical and automatic configuration
verification approach still remains an open problem.

\para{Language-support misconfiguration checking}
There have been several language-support efforts proposed for preventing
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in the network
configuration management area, administrators often
produce configuration errors in their routing configuration files.
PRESTO~\cite{enck07configuration} 
automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
routing protocols in a declarative fashion. 
COOLAID~\cite{chen10declarative} constructs
a language to describe domain knowledge about devices and
services for convenient network reasoning and management.
Compared with the above efforts, our work focuses on software systems, 
\eg, MySQL and Apache, and our main purpose is to automate configuration
verification rather than proposing new languages 
to convenient configuration-file writing.

\para{Misconfiguration detection}
Misconfiguration detection techniques aim at checking configuration
efforts before system outages occur.
Most existing detection approaches check 
the configuration files against a set of predefined correctness 
rules, named constraints, and then report errors if 
the checked configuration files do not satisfy these rules.
Huang {\em et al.}~\cite{huang15confvalley},
for example, proposed a 
language, ConfValley, to validate 
whether given configuration files meet administrators' specifications. 
As opposed to our work, ConfValley does not
have inherent misconfiguration checking capability, since it only offers
a language representation and requires administrators to
manually write specifications, which is an error-prone
process. On the contrary, our work does not need users to manually
write anything.

Several machine learning-based misconfiguration detection efforts 
also have been proposed~\cite{yuan11context, zhang14encore, xu16early}.
EnCore~\cite{zhang14encore} introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that enforce learning to focus on patterns of interest.
In this way, EnCore filters out irrelevant information and reduces
false positives; moreover, the templates are able to express
system environment information that other machine learning
techniques cannot handle.
Compared with EnCore, \app has the following advantages.
First, \app does not rely on any template. 
Second, EnCore cannot detect missing entry errors, type errors,
ordering errors and fine-grained integer correlation errors,
but \app can detect all of them.
Finally, \app is a very automatic system, but
EnCore needs significant human interventions, \eg, system parameters
and templates.

PCheck~\cite{xu16early} aims to add configuration checking code to the system source code by emulating potential commands and behaviors of the system. 
This emulation is a ``white-box'' approach and requires access to the system's source code.
One drawback to this approach is that for some systems (\eg, ZooKeeper) whose behavior is 
hard to emulate, PCheck cannot automatically generate the corresponding checking code.
Due to the emulation based testing strategy, PCheck's scope is limited to reliability problems caused by misconfiguration parameters. 
In contrast, \app is a ``black-box'' approach and only requires a training set of configuration files to learn rules.
By using a rule learning strategy of examples, \app is able to detect general misconfiguration issues that are outside the scope of emulation testing (\eg memory or thread usage settings), including performance, security, availability and reliability.

\para{Misconfiguration diagnosis}
Misconfiguration diagnosis approaches have been proposed to address configuration problems post-mortem.
For example, ConfAid~\cite{attariyan10automating} 
and X-ray~\cite{attariyan12x-ray} use dynamic information
flow tracking to find possible configuration errors that may have resulted in
failures or performance problems. AutoBash~\cite{su07autobash} 
tracks causality and automatically fixes 
misconfigurations. Unlike \app, most misconfiguration
diagnosis efforts aim at finding errors after system
failures occur, which leads to prolonged recovery time.

>>>>

Static configuration verification has been proposed as an effective way  
to tackle misconfiguration problems~\cite{xu15systems}.
Nevertheless, a practical and automatic configuration
verification approach still remains an open problem.

%rewritten
\para{Language-support misconfiguration checking}
One approach to statically checking configuration files is to avoid the difficult and unstructured nature of configuration files in the first place.
To that end efforts have introduced special configuration languages that overcome the fundamental deficiencies in the existing untyped or low-level configuration languages. 
For example, network administrators often produce configuration errors in their routing configuration files.
PRESTO~\cite{enck07configuration} introduces configlets as a template language to automates the generation of device-native configurations.
Other work uses Datalog to reason about routing protocols in a declarative fashion~\cite{loo05declarative}. 
COOLAID~\cite{chen10declarative} is a domain specific language to describe knowledge about network devices and services.
In contrast to this approach, our main purpose is to automate configuration verification of existing configuration languages, rather than proposing new, more powerful languages.
This is largely motivated by the unwieldy amount of existing configuration files in industry production.
%Furthermore, new systems are likely to continue to support the simple, unstructured style of existing configuration files beacuse the

One approach to preemptive error detection is to use predefined constraints, or correctness rules, for checking.
After encoding these constraints, it is straightforward to report errors if a target configuration file does not satisfy these rules.
For example, ConfValley is specification language for administrators to provide constraints on their systems' configurations~\cite{huang15confvalley}. 
This approach requires that administrators manually write specifications - an error-prone and difficult process. 
In contrast, by using a learning approach, our work does not require users to manually write any specifications.

\para{Learning}
Using machine learning to tackle misconfiguration detection has also been explored~\cite{yuan11context, zhang14encore, xu16early}.
As an example, EnCore~\cite{zhang14encore} uses a rule learning approach, augmented with user provided templates, to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates that enforce learning to focus on patterns of interest and allow the problem to scale over larger training sets.
EnCore uses the templates to filters out configuration entries that are unlikely to cause errors to reduce false positives.
The templates are also used to directly encode system environment information that would not be contained in the training set for their machine learning.
Compared with EnCore, our approach does not rely on templates - everything is automatically generated.
Furthermore, none of the above approaches use the temporal ordering on the training set inside the learning process.

\para{White-box}
In our approach we assume a ``black-box'' model where we cannot access the system source code.
This is as opposed to a ``white-box'' model, where the source code is available and can leveraged in the configuration analysis.
Although this is a strong assumption, PCheck~\cite{xu16early} explores misconfiguration detection by adding configuration checking code directly in the system source code.
The system is then emulating with various potential configurations of the system.
One drawback to this approach is that for some systems (\eg, ZooKeeper) whose behavior is hard to emulate, PCheck cannot automatically generate the corresponding checking code.
Due to the emulation based testing strategy, PCheck's scope is limited to reliability problems caused by misconfiguration parameters. 
In contrast, \app is a ``black-box'' approach and only requires a training set of configuration files to learn rules.
By using the version space learning strategy of examples, we are also able to detect general misconfiguration issues that are outside the scope of emulation testing (\eg memory or thread usage settings), including performance, security, availability and reliability.

\iffalse
%TODO rewrite
\para{Misconfiguration diagnosis}
Misconfiguration diagnosis approaches have been proposed to address configuration problems post-mortem.
For example, ConfAid~\cite{attariyan10automating} 
and X-ray~\cite{attariyan12x-ray} use dynamic information
flow tracking to find possible configuration errors that may have resulted in
failures or performance problems. AutoBash~\cite{su07autobash} 
tracks causality and automatically fixes 
misconfigurations. Unlike \app, most misconfiguration
diagnosis efforts aim at finding errors after system
failures occur, which leads to prolonged recovery time.
\fi
